Figures to insert in text

### 2018-04-04 kanerva-answer.tex
details

Dr. Kanerva writes\footnote{Email thread `SDM: A puzzling issue and an invitation', started March 16th 2018, in which we discussed the aforementioned discrepancy.}:

@@

Applying the law of total average, $\mathbf{E}[Z] = \mathbf{E}[\mathbf{E}[Z | h]] = \mathbf{E}[ph] = p \mathbf{E}[h] = p \mu_h$.

>>>>

Kanerva writes\footnote{Email thread `SDM: A puzzling issue and an invitation', started March 16th 2018, in which we discussed the aforementioned discrepancy.  To think that some centuries ago, all scientific publishing was the exchange of such letters.}:

@@

By the central limit theorem, $Z$ is normally distributed.

Applying the law of total averages and the law of total variance, $\mathbf{E}[Z] = \mathbf{E}[\mathbf{E}[Z | h]] = \mathbf{E}[ph] = p \mathbf{E}[h] = ph$, and $\mathbf{V}[Z] = \mathbf{E}[\mathbf{V}[Z|h]] + \mathbf{V}[\mathbf{E}[Z|h]] = \mathbf{E}[hp(1-p)] + \mathbf{V}[ph] = p(1-p) \mathbf{E}[h] + p^2 \mathbf{V}[h] = hp(1-p) + p^2 H p_1 (1-p_1)$.
